Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_review.Rmd
hide output from knitted product

```{r eval = TRUE, echo=FALSE, warning=FALSE}
#READING IN TABLES TO GET STATS FOR TEXT
path_to_ForC <- paste0(dirname(dirname(getwd())), "/ForC/") # this is to allow anybody to knit (assuming current working directory is in forc-db/ERL-review/manuscript and its "nesting" withing the ForC repo does not change)

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#READING IN TABLES TO GET STATS FOR TEXT
path_to_ForC <- paste0(dirname(dirname(getwd())), "/ForC/") # this is to allow anybody to knit (assuming current working directory is in forc-db/ERL-review/manuscript and its "nesting" withing the ForC repo does not change)
